---
title: "DC1_Exploratory"
author: "Esa Schenck"
date: "3/5/2021"
output: html_document
---

Exploratory Data Analysis

library(tidyverse)
library(readxl)

# Read phone log
phone_log <- read_excel("EditedPhoneLogR.xlsx")
View(phone_log)

# Filter days with no calls
call_days <- phone_log %>% 
  filter(!is.na(`Number Called`))
View(call_days)

# Sum number of calls to each number 
call_count <- call_days %>% 
  group_by(`Number Called`, Type) %>% 
  summarize(count = n())
View(call_count)

# All calls to city attorney 
attorney <- call_days %>% 
  filter(Type == "City Attorney")
View(attorney)

# All articles
articles <- read_csv("articlesTextDate.csv")
View(articles)

filter(articles, grepl('Switzerland',text))

filter(articles, grepl('Swiss',text))

filter(articles, grepl("2002",date))

filter(articles, grepl("VonRyker",text))

filter(articles, grepl("Delwin",text))

----------------------------------------------------
# Voter Registry Data

VoterRegistry <- read_xls("VoterRegistry.xls", col_names = TRUE)
VoterRegistryDF <- data.frame(VoterRegistry)

# Check for any values other than SYNTHETIC DATASET in first column
(TRUE %in% (VoterRegistryDF[[1]] != "SYNTHETIC DATASET"))

# Delete first column
VoterRegistryDF <- VoterRegistryDF[,-1]

# Making all first names uppercase
VoterRegistryDF$FIRST.NAME <- toupper(VoterRegistryDF$FIRST.NAME)

# Making all POB uppercase
VoterRegistryDF$POB <- toupper(VoterRegistryDF$POB)
head(VoterRegistryDF)

# Try to fix DOB format
typeof(VoterRegistryDF$DOB)
#VoterRegistryDF$DOB <- as.Date(VoterRegistryDF$VOTER.REG.DATE, "%m/%d/%Y %H:%M:%S")

#a <- as.Date(VoterRegistryDF$DOB)
#b <- as.Date(VoterRegistryDF$DOB,format="%d-%b-%y")
#a[is.na(a)] <- b[!is.na(b)]
#head(a, n=8)
#VoterRegistryDF$DOB <- a

#a <- as.Date(VoterRegistryDF$DOB,origin="1899-12-30")
#b <- as.Date(VoterRegistryDF$DOB,format="%d-%b-%y", origin="1899-12-30")
#head(a, n=8)
#head(b, n=8)

#mdy <- mdy(VoterRegistryDF$DOB)
#dmy <- dmy(VoterRegistryDF$DOB)
#mdy[is.na(mdy)] <- dmy[is.na(mdy)]

#VoterRegistryDF$DOB <- parse_date_time(VoterRegistryDF$DOB, orders=c('mdy', 'dmy'))

#VoterRegistryDF$DOB <- as.Date(VoterRegistryDF$DOB, origin="1899-12-30")

typeof(VoterRegistryDF$DOB)
head(VoterRegistryDF, n=8)



------------------------- Nage ------ News analysis

```{r}
fullTextdf <- readr::read_csv("fullTextdf.csv")
fullTextdf <- fullTextdf %>%
  mutate(strings.cleaned = gsub("[-.)(+]|[a-zA-Z]*:?","", text),
         date = strapplyc(strings.cleaned, "\\d+/\\d+/\\d+", simplify = TRUE))

fullTextdf <- fullTextdf %>%
  mutate(number = ex_number(strings.cleaned))
```

# Filter out news articles
```{r cow related news}
cow_news <- fullTextdf %>%
  filter(str_detect(text,"bovine"))

investigation <- fullTextdf %>%
  filter(str_detect(text,"FDA|investigation|Boynton"))

torch <-  fullTextdf %>%
  filter(str_detect(text,"voting"))
```

----------------------------------------------------------
